---
title: "Correlation Analysis: Income and Broadband Access"
author: "Edward Xu"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Introduction
This analysis examines the correlation between changes in median income and broadband access from 2017 to 2018.

## Load Required Libraries
```{r libraries}
library(readxl)
library(dplyr)
library(ggplot2)
```

## Import Data
```{r import}
# Read Excel data
income_data <- read_excel("C:/Users/tomat/Documents/income 2017-2018.xlsx")
broadband_data <- read_excel("C:/Users/tomat/Documents/leading zeros broadband.xlsx")

# Join datasets
combined_data <- income_data %>%
  left_join(broadband_data, by = "cfips")
```

## Correlation Analysis
```{r correlation}
# Calculate correlation
correlation_test_2018 <- cor.test(as.numeric(combined_data$`Median Household Income 2018`),
                                combined_data$broadband2018,
                                use = "complete.obs",
                                method = "pearson")

correlation_test_changes <- cor.test(combined_data$`Percent Change 2017-2018`,
                                   combined_data$change,
                                   use = "complete.obs",
                                   method = "pearson")

cor.test(as.numeric(combined_data$`Median Household Income 2018`),
         combined_data$broadband2018,
         use = "complete.obs")
```

## Results
```{r results}
# Correlation between median income and broadband access.
cat(sprintf("2018 Income and Broadband: r = %.3f (p < %.3e)\n", 
           correlation_test_2018$estimate, correlation_test_2018$p.value))

# Correlation between changes in median income and broadband access between 2017 and 2018.
cat(sprintf("2017-2018 Changes: r = %.3f (p = %.3f)\n", 
           correlation_test_changes$estimate, correlation_test_changes$p.value))
```

## Summary
The analysis shows a strong positive correlation between median income and broadband access in 2018 (r = 0.742, p < 0.001). However, when examining year-over-year changes from 2017 to 2018, there is virtually no correlation between changes in median income and broadband access (r = 0.003, p = 0.919). This suggests that while higher-income counties tend to have better broadband access, short-term changes in income are not associated with changes in broadband access.
